---
title: "What you see depends on what you hear"
subtitle: "Temporal rate averaging and crossmodal integration"
author: "Lihan Chen, Xiaolin Zhou, Hermann J. Mueller, Zhuanghua Shi"
output: 
  pdf_document: 
    fig_caption: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
suppressWarnings(suppressMessages(suppressPackageStartupMessages({
  source("ana_functions.R")})))
```

## Experiment 1 - Regular auditory sequence and Visual Ternus apparent motion (TAM)

Estimate TAM transitional thresholds with `quickpsy`. 
```{r exp1psy, echo=FALSE, fig.height=3, fig.width=4}
# due to lapsing and guessing, some participants may not have perfect psychometric curves
# so we estimate these two parameters as well. 
quickpsy(raw_data$Regular, x = soa, k = resp, grouping = .(sub), within = .(mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp1

# select 1 participant for an example
quickpsy(raw_data$Regular %>% filter(sub == 21), x = soa, k = resp,  within = .(mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp1sub1
fig2a <- plotcurves(exp1sub1, threshold = FALSE) + legend_pos(c(0.2,0.75)) + xlab ('ISI (ms') +   ylab('Prop. of group motion')
fig2a

```

* Mean PSEs
```{r exp1pses}
exp1$thresholds  %>% group_by(mIntv) %>% summarise(mpse = mean(thre)) %>% knitr::kable(.)

```

* ANOVAs and posthoc analysis

```{r exp1stats}
exp1$thresholds %>% ezANOVA(data =., dv = thre, wid = sub, within = mIntv) %>% knitr::kable(.)

# posthoc analysis
lme_exp1 = lme(thre ~ mIntv, data = exp1$thresholds, random = ~1|sub)
anova(lme_exp1)
summary(glht(lme_exp1, linfct = mcp(mIntv = 'Tukey')), test = adjusted(type = 'bonferroni'))
# posthoc suggest that significance between -70 and 0, -70 and 70, but not 70 and 0 conditions

```

* Mean JNDs and statistical summary:

```{r exp1jnd}
# mean JND (sigma)
exp1$par %>% filter(parn == 'p2') %>% group_by(mIntv) %>% summarise(msig = mean(par), se = sd(par)/sqrt(nlevels(sub)))
lme_exp1sig = lme(par ~ mIntv, data =exp1$par %>% filter(parn == 'p2'), random = ~1|sub)
anova(lme_exp1sig)
summary(glht(lme_exp1sig, linfct = mcp(mIntv = 'Tukey')), test = adjusted(type = 'bonferroni'))

```

## Experiment 2: With irregular auditory sequences

* A typical example from Experiment 2. 

```{r exp2psy, fig.height=3, fig.width=4}
# irregular, individual pses
quickpsy(raw_data$Irregular, x = soa, k = resp, grouping = .(sub), within = .(mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp2

# select 1 participant
quickpsy(raw_data$Irregular %>% filter(sub == 13), x = soa, k = resp,  within = .(mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp2sub1
fig2b <- plotcurves(exp2sub1, threshold = FALSE) + legend_pos(c(0.2,0.75)) + xlab ('ISI (ms') + 
  ylab('Prop. of group motion')
fig2b
```

* Statistics and tests:

```{r exp2stats}
# plot means and ANOVA analysis
exp2$thresholds  %>% group_by(mIntv) %>% summarise(mpse = mean(thre))
exp2$thresholds %>% ezANOVA(data =., dv = thre, wid = sub, within = mIntv)

# posthoc analysis
lme_exp2 = lme(thre ~ mIntv, data = exp2$thresholds, random = ~1|sub)
anova(lme_exp2)
summary(glht(lme_exp2, linfct = mcp(mIntv = 'Tukey')), test = adjusted(type = 'bonferroni'))
# same story: signicances between -70 and 0, -70 and 70, but not 70 and 0. 
# mean JND (sigma)
exp2$par %>% filter(parn == 'p2') %>% group_by(mIntv) %>% summarise(msig = mean(par), se = sd(par)/sqrt(nlevels(sub)))
lme_exp2sig = lme(par ~ mIntv, data =exp2$par %>% filter(parn == 'p2'), random = ~1|sub)
anova(lme_exp2sig)
summary(glht(lme_exp2sig, linfct = mcp(mIntv = 'Tukey')), test = adjusted(type = 'bonferroni'))

```


* Figure 2 with combination of Experiments 1 and 2, mean PSEs and typical psychometric curves. 

```{r fig2, fig.cap = 'Typical examples and mean PSEs from Exp. 1 and 2'}
# add signficance to the bar figure. 
fig2c <- exp1$thresholds %>% rename(pse = thre) %>% psebar(.)

fig2c <- fig2c + geom_signif(comparisons = list(c('-70','0')), annotation = '*', color = 'black') + 
  geom_signif(comparisons = list(c('-70','70')), annotation = '*', y_position = 160, color = 'black')

# create average bar plots
fig2d <- exp2$thresholds %>% rename(pse = thre) %>% psebar(.)
fig2d <- fig2d + geom_signif(comparisons = list(c('-70','0')), annotation = '*', color = 'black') + 
  geom_signif(comparisons = list(c('-70','70')), annotation = '*', y_position = 170, color = 'black')

fig2 <- plot_grid(fig2a,fig2b, fig2c, fig2d, nrow = 2, labels = c('A','B','C','D'))
fig2
#ggsave('figure2.pdf',fig2, width=8, height = 6)

```

## Experiment 3: Variance manipulation

* Plot mean results of PSEs as functions of variances and mean auditory intervals. 

```{r exp3pse, fig.height=3, fig.width=4}
# variance manipulation experiment
quickpsy(raw_data$Variance, x = soa, k = resp, grouping = .(sub), within = .(var, mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp3

# plot means and ANOVA analysis
exp3$thresholds %>%  group_by(var, mIntv) %>% summarise(mpse = mean(thre), se = sd(thre)/sqrt(nlevels(sub)-1)) -> mexp3
exp3$thresholds  %>% ezANOVA(data =., dv = thre, wid = sub, within = .(var, mIntv))

fig3 <- ggplot(mexp3, aes(mIntv, mpse, ymin = mpse - se, ymax = mpse + se, color = var, group = var)) + 
  geom_line() + geom_errorbar(width = 0.2) + geom_point() + legend_pos(c(0.8,0.8)) + 
  xlab('Relative mean auditory intervals (ms)') + ylab('PSEs (ms)')
fig3
#ggsave(filename = 'figure3.pdf', fig3, width = 6, height = 4)
```

* Statistical tests:

```{r exp3stats, fig.height=3, fig.width=4}
# posthoc analysis
lme_exp3 = lme(thre ~ mIntv * var, data = exp3$thresholds, random = ~1|sub)
anova(lme_exp3)
summary(glht(lme_exp3, linfct = mcp(mIntv = 'Tukey')), test = adjusted(type = 'bonferroni'))

```

## Experiment 4: Geometric vs. Arithmetic mean

* Estimate thresholds and show a typical example. 


* Figure 4

```{r fig4, fig.height=3, fig.width=6}
# arithmetic one
quickpsy(raw_data$Geometry, x = soa, k = resp, grouping = .(sub), within = .(mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp4
# select one participant
quickpsy(raw_data$Geometry %>% filter(sub == 6), x = soa, k = resp, within = .(mIntv), 
         lapses = TRUE, guess = TRUE, bootstrap = 'none', 
         parini = list(c(1,250),c(1,200),c(0,0.3),c(0,0.3))) -> exp4sub1
fig4a <- plotcurves(exp4sub1, threshold = FALSE) + legend_pos(c(0.2,0.75)) + xlab ('ISI (ms') + 
  ylab('Prop. of group motion')# combine two subplots together into Figure 4

# plot bar figure with significances
fig4b <- exp4$thresholds %>% rename(pse = thre) %>% psebar(.)
fig4b <- fig4b + geom_signif(comparisons = list(c('GeoM','AriM')), annotation = '*', y_position = 165, color = 'black') + 
  geom_signif(comparisons = list(c('GeoM','Equal')), annotation = '*', y_position = 160, color = 'black')

fig4 <- plot_grid(fig4a,fig4b, nrow = 1, labels = c('A','B'))
fig4
#ggsave(filename = 'figure4.pdf', fig4, width = 8, height = 4)
```

* Statistical tests

```{r exp4stats, echo = TRUE}
# plot means and ANOVA analysis
exp4$thresholds  %>% group_by( mIntv) %>% summarise(mpse = mean(thre), se = sd(thre)/sqrt(nlevels(sub)-1)) -> mexp4
exp4$thresholds  %>% ezANOVA(data =., dv = thre, wid = sub, within = .( mIntv))
# posthoc analysis
lme_exp4 = lme(thre ~ mIntv, data = exp4$thresholds, random = ~1|sub)
anova(lme_exp4)
summary(glht(lme_exp4, linfct = mcp(mIntv = 'Tukey')), test = adjusted(type = 'bonferroni'))

```

## Bayesian modeling of audiovisual integration

The detailed model is described in the main text of the paper (see also some comments in `ana_functions.R`). 

```{r preprocess_model}

# read mean responses from formal experiments, together with the baseline conditions
meanResps <- readRDS('meanResps.rds')

# ---- integration_model ----
# note, running optimization may take several minutes
# please use the following flag `runOptim` to control it
runOptim = FALSE
if (runOptim){
  resp.predicted <- predictResp(meanResps) # partial integration
  resp.fullfusion <- predictResp(meanResps, FALSE)# full integration
  saveRDS(resp.predicted,'partial_integration_new.rds')
  saveRDS(resp.fullfusion,'full_integration_new.rds')
}else{
  resp.predicted <- readRDS('partial_integration_new.rds')
  resp.fullfusion <- readRDS('full_integration_new.rds')
}

```

* Comparison among partial and full models:

```{r model_comparison}

# sse, r^2, BIC
stat1 <- resp.predicted %>% group_by(exp) %>% 
  summarise(sse = sum((m-mresp)^2), 
            sst = sum((m- mean(resp.fullfusion$m))^2), 
            n = n()) %>% 
  mutate(bic_partial = n*log(sse/n) + 2*log(n), r2_partial = 1-sse/sst)

stat2 <- resp.fullfusion %>% group_by(exp) %>% 
  summarise(sse = sum((m-mresp)^2), 
            sst = sum((m- mean(resp.fullfusion$m))^2), 
            n = n()) %>% 
  mutate(bic_full = n*log(sse/n) + 2*log(n), r2_full = 1 - sse/sst)

stat_tab <- left_join(stat1, stat2, by = c('exp')) %>% 
  mutate(delta = bic_full - bic_partial) %>%
  dplyr::select(exp, bic_partial, r2_partial, bic_full, r2_full, delta) 
colnames(stat_tab) <- c("Exp.", "BIC P.I.", "R2 P.I.", 
                        "BIC F.I.", "R2 F.I.", "BIC Diff.")

knitr::kable(stat_tab, digits=2)
```

* Predicted average responses versus empirical results. 

```{r modresp, fig.height=6, fig.width=6}
# plot predicted responses
resp.predicted %>%
  #resp.fullfusion%>%
  group_by(cond, mIntv,soa ) %>%
  summarise(mr = mean(m), mse = mean(mse),
            mpred = mean(mresp)) %>% 
  ggplot(aes(soa, y = mr,  shape = mIntv, color = mIntv, linetype = mIntv)) + geom_point(size = 2) + 
  geom_line(aes(y=mpred)) + 
  geom_errorbar(aes(x = soa, ymin = mr - mse, ymax = mr + mse), width = 5) + 
  scale_shape(solid = FALSE) + xlab('ISI (ms)') + 
  ylab('Prop. of group motion')+  facet_wrap(~cond, nrow = 2) + figTheme()
```

* Plot mean weights

```{r modw, fig.height=3, fig.width=6}
# predict weights as function SOA
resp.predicted %>% group_by(exp, mIntv, soa) %>% summarise(mw = mean(w)) %>% 
  ggplot(aes(x = soa, y = mw, color = mIntv, linetype = mIntv, shape = mIntv)) + geom_line() + 
  geom_point(size = 2) +facet_wrap(~exp) + xlab('ISI (ms)') + ylab('Means auditory weights') + 
  scale_shape(solid = FALSE) + figTheme()
```

* Show predicted vs. behavioral results. 

```{r modpred, fig.height=3, fig.width=4}
pse.predicted <- predictPSEnew(resp.predicted)
#pse.predicted <- predictPSE(resp.fullfusion)
# the following is to obtain slope 0.978 and R^2= 0.983
pse.lm <- pse.predicted %>% 
  lm( ppse ~ pse -1, data = .)
summary(pse.lm)
fig_pses <- pse.predicted %>% 
  group_by(exp, mIntv) %>% #summarise(pse = mean(pse), ppse = mean(ppse)) %>%
  ggplot(., aes(x=pse, y = abs(ppse), shape = exp)) + geom_point() +geom_abline(slope = 1, linetype = 'dashed') + xlab('Observed PSEs (ms)') + ylab('Predicted PSEs (ms)')+ 
  figTheme() 
fig_pses
```

